Analysis and elimination of bottlenecks in parallel algorithm for solving global optimization problems

### 2022-04-13 2022/RSD/paper.tex
Добавлены картинки.

\begin{table}[ht]
	\caption{Number of trials executed by Hooke-Jeeves method}
	\label{tab:1}
	\center
	\begin{tabular}{|c|c|c|c|c|c|}
		\hline
		%\noalign{\smallskip}
		N & P = 1 & P = 2 & P = 4 & P = 8 & P = 16 \\
		\hline 
		2 &	 &  &  &  &   \\
		\hline
		3 &	 &  &  &  &   \\
		\hline
		5 &	 &  &  &  &   \\
		\hline
		10 &  &  &  &  &   \\
		\hline
		15 &  &  &  &  &   \\
		\hline
		30 &  &  &  &  &   \\
		\hline
	\end{tabular}
\end{table}

\begin{table}[ht]
	\caption{Speedup when using Hooke-Jeeves method}
	\label{tab:2}
	\center
	\begin{tabular}{|c|c|c|c|c|}
		\hline
		%\noalign{\smallskip}
		N & P = 2 & P = 4 & P = 8 & P = 16 \\
		\hline 
		2 &  &  &  &   \\
		\hline
		3 &  &  &  &   \\
		\hline
		5 &  &  &  &   \\
		\hline
		10 &  &  &  &   \\
		\hline
		15 &  &  &  &   \\
		\hline
		30 &  &  &  &   \\
		\hline
	\end{tabular}
\end{table}

\begin{table}[ht]
	\caption{Number of trials executed by BFGS method}
	\label{tab:3}
	\center
	\begin{tabular}{|c|c|c|c|c|c|}
		\hline
		%\noalign{\smallskip}
		N & P = 1 & P = 2 & P = 4 & P = 8 & P = 16 \\
		\hline 
		2 &	 &  &  &  &   \\
		\hline
		3 &	 &  &  &  &   \\
		\hline
		5 &	 &  &  &  &   \\
		\hline
		10 &  &  &  &  &   \\
		\hline
		15 &  &  &  &  &   \\
		\hline
		30 &  &  &  &  &   \\
		\hline
	\end{tabular}
\end{table}

\begin{table}[ht]
	\caption{Speedup when using BFGS method}
	\label{tab:4}
	\center
	\begin{tabular}{|c|c|c|c|c|}
		\hline
		%\noalign{\smallskip}
		N & P = 2 & P = 4 & P = 8 & P = 16 \\
		\hline 
		2 &  &  &  &   \\
		\hline
		3 &  &  &  &   \\
		\hline
		5 &  &  &  &   \\
		\hline
		10 &  &  &  &   \\
		\hline
		15 &  &  &  &   \\
		\hline
		30 &  &  &  &   \\
		\hline
	\end{tabular}
\end{table}

@@

\begin{table}[ht]
	\caption{Averaged number of iterations for AGS algorithm}
	\label{tab:5}
	\center
	\begin{tabular}{|c|c|c|c|c|c|c|}
		\hline
		N & Problem class & P = 1 & P = 2 & P = 4 & P = 8 & P = 16 \\
		\hline 
		    \multirow{2}{*}{4} & hard &  &  &  &  &  \\ \cline{2-7}
		                       & simple &  &  &  &  &  \\
		\hline
		    \multirow{2}{*}{5} & hard &  &  &  &  &  \\ \cline{2-7}
		                       & simple &  &  &  &  &  \\
		\hline
	\end{tabular}
\end{table}

\begin{table}[ht]
	\caption{Averaged number of trials executed by Hooke-Jeeves method}
	\label{tab:6}
	\center
	\begin{tabular}{|c|c|c|c|c|c|c|}
		\hline
		N & Problem class & P = 1 & P = 2 & P = 4 & P = 8 & P = 16 \\
		\hline 
		    \multirow{2}{*}{4} & hard &  &  &  &  &  \\ \cline{2-7}
		                       & simple &  &  &  &  &  \\
		\hline
		    \multirow{2}{*}{5} & hard &  &  &  &  &  \\ \cline{2-7}
		                       & simple &  &  &  &  &  \\
		\hline
	\end{tabular}
\end{table}

\begin{table}[ht]
	\caption{Speedup when using Hooke-Jeeves method}
	\label{tab:7}
	\center
	\begin{tabular}{|c|c|c|c|c|c|}
		\hline
		N & Problem class  & P = 2 & P = 4 & P = 8 & P = 16 \\
		\hline 
		    \multirow{2}{*}{4} & hard &  &  &  &  \\ \cline{2-6}
		                       & simple &  &  &  &  \\
		\hline
		    \multirow{2}{*}{5} & hard &  &  &  &  \\ \cline{2-6}
		                       & simple &  &  &  &  \\
		\hline
	\end{tabular}
\end{table}

\begin{table}[ht]
	\caption{Averaged number of trials executed by BFGS method}
	\label{tab:8}
	\center
	\begin{tabular}{|c|c|c|c|c|c|c|}
		\hline
		N & Problem class & P = 1 & P = 2 & P = 4 & P = 8 & P = 16 \\
		\hline 
		    \multirow{2}{*}{4} & hard &  &  &  &  &  \\ \cline{2-7}
		                       & simple &  &  &  &  &  \\
		\hline
		    \multirow{2}{*}{5} & hard &  &  &  &  &  \\ \cline{2-7}
		                       & simple &  &  &  &  &  \\
		\hline
	\end{tabular}
\end{table}

\begin{table}[ht]
	\caption{Speedup when using BFGS method}
	\label{tab:9}
	\center
	\begin{tabular}{|c|c|c|c|c|c|c|}
		\hline
		N & Problem class & P = 1 & P = 2 & P = 4 & P = 8 & P = 16 \\
		\hline 
		    \multirow{2}{*}{4} & hard &  &  &  &  &  \\ \cline{2-7}
		                       & simple &  &  &  &  &  \\
		\hline
		    \multirow{2}{*}{5} & hard &  &  &  &  &  \\ \cline{2-7}
		                       & simple &  &  &  &  &  \\
		\hline
	\end{tabular}
\end{table}

\begin{table}[ht]
	\caption{Speedup when using BFGS method}
	\label{tab:10}
	\center
	\begin{tabular}{|c|c|c|c|c|c|}
		\hline
		N & Problem class  & P = 2 & P = 4 & P = 8 & P = 16 \\
		\hline 
		    \multirow{2}{*}{4} & hard &  &  &  &  \\ \cline{2-6}
		                       & simple &  &  &  &  \\
		\hline
		    \multirow{2}{*}{5} & hard &  &  &  &  \\ \cline{2-6}
		                       & simple &  &  &  &  \\
		\hline
	\end{tabular}
\end{table}

@@

Table XX presents the total time of solving four problems corresponding to four different temperature regimes.
\begin{table}[ht]
	\caption{Averaged time of solving the problem, sec.}
	\label{tab:11}
	\center
		\begin{tabular}{|c|c|c|c|c|}
		\hline
		%\noalign{\smallskip}
		Method & P = 1 & P = 3 & P = 5 & P = 15 \\
		\hline 
		Hooke-Jeeves &  &  &  &   \\
		\hline
		L-BFGS-B &  &  &  &   \\
		\hline
	\end{tabular}
\end{table}

@@

\begin{table}[ht]
	\caption{Time of solving the problem using a local method}
	\label{tab:12}
	\center
		\begin{tabular}{|c|c|c|c|}
		\hline
		%\noalign{\smallskip}
		Method & GSA & GSA-l & GSA-pl \\
		\hline 
		Hooke-Jeeves &  &  &   \\
		\hline
		L-BFGS-B &  &  &   \\
		\hline
	\end{tabular}
\end{table}

>>>>

%\begin{table}[ht]
%	\caption{Number of trials executed by Hooke-Jeeves method}
%	\label{tab:1}
%	\center
%	\begin{tabular}{|c|c|c|c|c|c|}
%		\hline
%		%\noalign{\smallskip}
%		N & P = 1 & P = 2 & P = 4 & P = 8 & P = 16 \\
%		\hline 
%		2 &	 &  &  &  &   \\
%		\hline
%		3 &	 &  &  &  &   \\
%		\hline
%		5 &	 &  &  &  &   \\
%		\hline
%		10 &  &  &  &  &   \\
%		\hline
%		15 &  &  &  &  &   \\
%		\hline
%		30 &  &  &  &  &   \\
%		\hline
%	\end{tabular}
%\end{table}
%
%\begin{table}[ht]
%	\caption{Speedup when using Hooke-Jeeves method}
%	\label{tab:2}
%	\center
%	\begin{tabular}{|c|c|c|c|c|}
%		\hline
%		%\noalign{\smallskip}
%		N & P = 2 & P = 4 & P = 8 & P = 16 \\
%		\hline 
%		2 &  &  &  &   \\
%		\hline
%		3 &  &  &  &   \\
%		\hline
%		5 &  &  &  &   \\
%		\hline
%		10 &  &  &  &   \\
%		\hline
%		15 &  &  &  &   \\
%		\hline
%		30 &  &  &  &   \\
%		\hline
%	\end{tabular}
%\end{table}
%
%\begin{table}[ht]
%	\caption{Number of trials executed by BFGS method}
%	\label{tab:3}
%	\center
%	\begin{tabular}{|c|c|c|c|c|c|}
%		\hline
%		%\noalign{\smallskip}
%		N & P = 1 & P = 2 & P = 4 & P = 8 & P = 16 \\
%		\hline 
%		2 &	 &  &  &  &   \\
%		\hline
%		3 &	 &  &  &  &   \\
%		\hline
%		5 &	 &  &  &  &   \\
%		\hline
%		10 &  &  &  &  &   \\
%		\hline
%		15 &  &  &  &  &   \\
%		\hline
%		30 &  &  &  &  &   \\
%		\hline
%	\end{tabular}
%\end{table}
%
%\begin{table}[ht]
%	\caption{Speedup when using BFGS method}
%	\label{tab:4}
%	\center
%	\begin{tabular}{|c|c|c|c|c|}
%		\hline
%		%\noalign{\smallskip}
%		N & P = 2 & P = 4 & P = 8 & P = 16 \\
%		\hline 
%		2 &  &  &  &   \\
%		\hline
%		3 &  &  &  &   \\
%		\hline
%		5 &  &  &  &   \\
%		\hline
%		10 &  &  &  &   \\
%		\hline
%		15 &  &  &  &   \\
%		\hline
%		30 &  &  &  &   \\
%		\hline
%	\end{tabular}
%\end{table}

\begin{figure}
\begin{center}
  \includegraphics[width=1.0\linewidth]{RosenbrocNT.jpg}
  \caption{Number of trials executed on the Rosenbrock function}
  \label{fig:RosenbrocNT}  
\end{center}
\end{figure}

\begin{figure}
\begin{center}
  \includegraphics[width=1.0\linewidth]{RosenbrocSpeedup.jpg}
  \caption{Speedup on the Rosenbrock function}
  \label{fig:RosenbrocSpeedup}  
\end{center}
\end{figure}

@@

\begin{table}[ht]
	\caption{Averaged number of iterations for AGS algorithm}
	\label{tab:5}
	\center
	\begin{tabular}{|c|c|c|c|c|c|c|}
		\hline
		N & Problem class & P = 1 & P = 2 & P = 4 & P = 8 & P = 16 \\
		\hline 
		    \multirow{2}{*}{4} & hard & 36528 & 18651 & 9854 & 4808 & 2260 \\ \cline{2-7}
		                       & simple & 9995 & 5199 & 2706 & 1333 & 630 \\
		\hline
		    \multirow{2}{*}{5} & hard & 266420 & 149109 & 90894 & 39873 & 22206 \\ \cline{2-7}
		                       & simple & 29853 & 12913 & 7296 & 3618 & 2220 \\
		\hline
	\end{tabular}
\end{table}

%\begin{table}[ht]
%	\caption{Averaged number of trials executed by Hooke-Jeeves method}
%	\label{tab:6}
%	\center
%	\begin{tabular}{|c|c|c|c|c|c|c|}
%		\hline
%		N & Problem class & P = 1 & P = 2 & P = 4 & P = 8 & P = 16 \\
%		\hline 
%		    \multirow{2}{*}{4} & hard &  &  &  &  &  \\ \cline{2-7}
%		                       & simple &  &  &  &  &  \\
%		\hline
%		    \multirow{2}{*}{5} & hard &  &  &  &  &  \\ \cline{2-7}
%		                       & simple &  &  &  &  &  \\
%		\hline
%	\end{tabular}
%\end{table}
%
%\begin{table}[ht]
%	\caption{Speedup when using Hooke-Jeeves method}
%	\label{tab:7}
%	\center
%	\begin{tabular}{|c|c|c|c|c|c|}
%		\hline
%		N & Problem class  & P = 2 & P = 4 & P = 8 & P = 16 \\
%		\hline 
%		    \multirow{2}{*}{4} & hard &  &  &  &  \\ \cline{2-6}
%		                       & simple &  &  &  &  \\
%		\hline
%		    \multirow{2}{*}{5} & hard &  &  &  &  \\ \cline{2-6}
%		                       & simple &  &  &  &  \\
%		\hline
%	\end{tabular}
%\end{table}
%
%
%\begin{table}[ht]
%	\caption{Averaged number of trials executed by BFGS method}
%	\label{tab:8}
%	\center
%	\begin{tabular}{|c|c|c|c|c|c|c|}
%		\hline
%		N & Problem class & P = 1 & P = 2 & P = 4 & P = 8 & P = 16 \\
%		\hline 
%		    \multirow{2}{*}{4} & hard &  &  &  &  &  \\ \cline{2-7}
%		                       & simple &  &  &  &  &  \\
%		\hline
%		    \multirow{2}{*}{5} & hard &  &  &  &  &  \\ \cline{2-7}
%		                       & simple &  &  &  &  &  \\
%		\hline
%	\end{tabular}
%\end{table}
%
%
%\begin{table}[ht]
%	\caption{Speedup when using BFGS method}
%	\label{tab:10}
%	\center
%	\begin{tabular}{|c|c|c|c|c|c|}
%		\hline
%		N & Problem class  & P = 2 & P = 4 & P = 8 & P = 16 \\
%		\hline 
%		    \multirow{2}{*}{4} & hard &  &  &  &  \\ \cline{2-6}
%		                       & simple &  &  &  &  \\
%		\hline
%		    \multirow{2}{*}{5} & hard &  &  &  &  \\ \cline{2-6}
%		                       & simple &  &  &  &  \\
%		\hline
%	\end{tabular}
%\end{table}

\begin{figure}
\begin{center}
  \includegraphics[width=1.0\linewidth]{GKLSNT.jpg}
  \caption{Number of trials executed on the GKLS function}
  \label{fig:GKLSNT}  
\end{center}
\end{figure}

\begin{figure}
\begin{center}
  \includegraphics[width=1.0\linewidth]{GKLSSpeedup.jpg}
  \caption{Speedup on the GKLS function}
  \label{fig:GKLSSpeedup}  
\end{center}
\end{figure}

@@

Table XX presents the total time of solving four problems corresponding to four different temperature regimes.

\begin{table}[ht]
	\caption{Averaged time of solving the problem, sec.}
	\label{tab:11}
	\center
		\begin{tabular}{|c|c|c|c|}
		\hline
		%\noalign{\smallskip}
		Method & P = 1 & P = 3 &  P = 15 \\
		\hline 
		Hooke-Jeeves & 2386.4 & 1053.1 & 713.1  \\
		\hline
		L-BFGS-B & 2571.7  & 1096.4  & 720.3  \\
		\hline
	\end{tabular}
\end{table}

@@

\begin{table}[ht]
	\caption{Time of solving the problem using a local method}
	\label{tab:12}
	\center
		\begin{tabular}{|c|c|c|c|}
		\hline
		%\noalign{\smallskip}
		Method & GSA & GSA-l & GSA-pl \\
		\hline 
		Hooke-Jeeves & 158.1 & 299.8  & 177.4 \\
		\hline
		L-BFGS-B & 158.1  & 252.5  & 165.6  \\
		\hline
	\end{tabular}
\end{table}
